---
title: "challenge B final"
author: "Maxime TRANCHARD , Emma GAILLAT"
date: "7 décembre 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
``` 

Task 1B - Predicting house prices in Ames, Iowa
```{r load packages, message=FALSE, warning=FALSE, include=FALSE}
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
install.packages("readr",repos = "http://cran.us.r-project.org")
install.packages("randomForest",repos = "http://cran.us.r-project.org")
install.packages("np",repos = "http://cran.us.r-project.org")
install.packages("data.table",repos = "http://cran.us.r-project.org")
library(randomForest)
library(data.table)
library(tidyverse)
library(readr)
library(dplyr)
library(np)
library(readxl)
```
```{r load packages no eval, eval=FALSE}
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
install.packages("readr",repos = "http://cran.us.r-project.org")
install.packages("randomForest",repos = "http://cran.us.r-project.org")
install.packages("np",repos = "http://cran.us.r-project.org")
install.packages("data.table",repos = "http://cran.us.r-project.org")
library(randomForest)
library(data.table)
library(tidyverse)
library(readr)
library(dplyr)
library(np)
library(readxl)
```
STEP 1) 
we choose to run a randomForest prediction. Random forests or random decision forests are an ensemble learning method for classification, regression and other tasks, that operate by constructing a multitude of decision trees at training time and outputting the class that is the mode of the classes (classification) or mean prediction (regression) of the individual trees. Random decision forests correct for decision trees' habit of overfitting to their training set. This is better with a lot of observations. Here it's the case so we assume it suits. 

STEP 2)
```{r DAta}
train<- read.csv("train.csv")
Test<- read.csv(file = "test.csv")
```

```{r step1, include=FALSE}
## we choose the randomForest ML technique 
colnames(train)
Train<-train[-1] 

```

```{r step 2, fig.height = 3, fig.width = 5, results="hide"}
na_count<-sapply(Train, function(y) sum(length(which(is.na(y)))))
na_count
```
We remove the columns where there are a lot of missing variables, and only after that we remove the rows where there are missing variables.
```{r no missing, echo=TRUE, results="hide"}
Train$PoolQC <- NULL
Train$Fence <- NULL
Train$MiscFeature <- NULL
Train$Alley <- NULL
Train$FireplaceQu <- NULL
Train$LotFrontage <- NULL
Train<- na.omit(Train)
```
Creating our prediction with RandomForest
```{r randomforest model, message=FALSE, warning=FALSE}
Train <-Train%>%mutate_if(is.character,as.factor)
names(Train)<-make.names(names(Train))  
set.seed(1)
Train.fit<-randomForest(Train$SalePrice~., data=Train)
Predict.RandomForest<-predict(Train.fit,data=Test) 
```


Step 3) Let's compare with a OLS 


```{r linear model, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
Train.lm<-lm(data=Train,SalePrice~.) 
predict.lr<-predict(print(Train.lm), data=Test)
```

```{r linear model Rcode, message=FALSE, warning=FALSE, include=FALSE}
Train.lm<-lm(data=Train,SalePrice~.) 
predict.lr<-predict(print(Train.lm), data=Test)
```

```{r compare}
summary(Predict.RandomForest) 
summary(predict.lr)

```

```{r compare next, fig.height = 3, fig.width = 5}
diff<-as.data.frame(Predict.RandomForest-predict.lr)
plot(diff)
ggplot()+geom_line(aes(predict.lr,Predict.RandomForest))+geom_line(aes(predict.lr,predict.lr),col="red")

```



Even if we can think the difference are really big, when we focus and the mean (where the ols is good), both are pretty similar moreover regarding the variations of the observations a variation of 10^4 is not that important for a house price.

TASK 2B - Overfitting in Machine Learning
remember first what we have done in Part A
```{r challenge A review, fig.height = 3, fig.width = 5}
set.seed(1)
xpaul <- 2
ypaul <- xpaul^3
x <- rnorm(n = 150)
e <- rnorm(n=150)
y <- x^3 + e
draws <- data.frame(y,x)
y <- function(x){x^3}
draws$idx <- sample(seq(FALSE, TRUE), size = nrow(draws), replace = TRUE, prob = c(.8, .2))
train <- draws[draws$idx == FALSE,]
test <- draws[draws$idx == TRUE,]
y_true<-train$x^3
```
We estimate a low-flexibility and a high-flexibility local linear model on the training data using the function npreg.
STEP 1)
```{r task2_step 1, results='hide'}
ll.fit.lowflex <- npreg(y ~ x, data = train, method = "ll", bws = 0.5)
summary(ll.fit.lowflex)
```
STEP 2)
```{r task2_step2, results='hide'}
ll.fit.highflex <- npreg(y ~ x, data = train, method = "ll", bws = 0.01)
summary(ll.fit.highflex)
```
STEP 3) 
```{r task2_step3, results='hide', fig.show='hide'}
#First, we compute the predictions for ll.fit.highflex and ll.fit.lowflex
fitted.highflex <- fitted(ll.fit.highflex)
fitted.lowflex <- fitted(ll.fit.lowflex)

#And now, we are able to plot.
graph1 <- ggplot() + geom_point(data=train, mapping = aes(x = x, y = y)) + geom_line(data=train, mapping = aes(x = x, y = y_true)) + geom_line(data=train, mapping = aes(x = x, y = fitted.highflex), color = "blue") + geom_line(data=train, mapping = aes(x = x, y = fitted.lowflex), color = "red")
graph1
```
STEP 4)
when we look at the graph we see that the model ll.fit.highflex is the prediction most variable, which has the lowest bandwidth. Also, we can compute the variance of each prediction and check this statement.
```{r task2_step4_Var, results='hide'}
variance <- cbind(var(y_true), var(fitted.highflex), var(fitted.lowflex))
colnames(variance) <- c("true model","highflex","lowflex")
variance
bias <- cbind(mean(y_true-train$y), mean(fitted.highflex-train$y), mean(fitted.lowflex-train$y))
colnames(bias) <- c("true model","highflex","lowflex")
abs(bias)
```
thus the highflex model is the one with less biais. 

STEP 5)  same as before but with Data = test
```{r task2_step5 , results='hide'}
ll.fit.lowflex.test <- npreg(y ~ x, data = test, method = "ll", bws = 0.5)
summary(ll.fit.lowflex.test)
ll.fit.highflex.test <- npreg(y ~ x, data = test, method = "ll", bws = 0.01)
summary(ll.fit.highflex.test)
y_true.test <- test$x^3

fitted.highflex.test <- fitted(ll.fit.highflex.test)
fitted.lowflex.test <- fitted(ll.fit.lowflex.test)

graph2 <- ggplot() +
  geom_point(data=test, mapping = aes(x = x, y = y)) + 
  geom_line(data=test, mapping = aes(x = x, y = y_true.test)) +
  geom_line(data=test, mapping = aes(x = x, y = fitted.highflex.test), color = "blue") +
  geom_line(data=test, mapping = aes(x = x, y = fitted.lowflex.test), color = "red")
graph2
variance.test <- cbind(var(y_true.test), var(fitted.highflex.test), var(fitted.lowflex.test))
colnames(variance.test) <- c("true model","highflex","lowflex")

variance.test
bias.test <- cbind(mean(y_true.test-test$y), mean(fitted.highflex.test-test$y), mean(fitted.lowflex.test-test$y))
colnames(bias.test) <- c("true model","highflex","lowflex")

abs(bias.test)

```
highflex remain the best but the bias rise. 

STEP 6) Creating a vector
```{r step 6}
bw <- seq(0.01, 0.5, by = 0.001)
```
STEP 7) Estimate a local linear model
```{r task2_step 7}
vector.fit<-lapply(X = bw, FUN = function(bw) {npreg(y ~ x, data = train, method = "ll", bws = bw)})
```
STEP 8) we compute the MSE
```{r step 7 - 8 }
train.mse <- function(fit.model){
predictions <- predict(object = fit.model, newdata = train)
train %>% mutate(squared.error = (y - predictions)^2) %>% summarize(mse = mean(squared.error))}
train.mse.output <- unlist(lapply(X = vector.fit, FUN = train.mse))
```

STEP 9) Lets do the same for the test Data.
```{r task_step 9}
test.mse <- function(model.fit){
estimations <- predict(object = model.fit, newdata = test)
test %>% mutate(squared.error = (y - estimations)^2) %>% summarize(mse = mean(squared.error))
}
test.mse.output <- unlist(lapply(X = vector.fit, FUN = test.mse))

```
Step 10) 
```{r task2_step 10}
mse.table <- tbl_df(data.frame(bandwidth = bw, train.mse = train.mse.output, test.mse = test.mse.output))
mse.table
ggplot(mse.table) + 
geom_line(mapping = aes(x = bandwidth, y = train.mse), color = "blue") +
geom_line(mapping = aes(x = bandwidth, y = test.mse), color = "orange")
```
0.2 is the point where we minimise our MSE for the test Data; No interest to go for a smaller one an decrease the MSE of the training data. 


TASK 3 - PRIVACY REGULATION COMPLIANCE IN FRANCE

STEP 1) Let's import our DATA.
```{r task3_step 1 code, fig.height = 3, fig.width = 5, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(readr)
library(readxl)
CNIL<-cil <- read.csv("https://www.data.gouv.fr/s/resources/correspondants-informatique-et-libertes-cil/20171115-183631/OpenCNIL_Organismes_avec_CIL_VD_20171115.csv", header=TRUE, sep = ";")
SIREN <- read_delim("sirc-17804_9075_14211_2017340_E_Q_20171207_022339046.csv", 
                                                                  ";", escape_double = FALSE, trim_ws = TRUE)
```
```{r task3_step 1, fig.height = 3, fig.width = 5, message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(readxl)
CNIL<-cil <- read.csv("https://www.data.gouv.fr/s/resources/correspondants-informatique-et-libertes-cil/20171115-183631/OpenCNIL_Organismes_avec_CIL_VD_20171115.csv", header=TRUE, sep = ";")
SIREN <- read_delim("sirc-17804_9075_14211_2017340_E_Q_20171207_022339046.csv", 
                                                                  ";", escape_double = FALSE, trim_ws = TRUE)
colnames(CNIL)
```

STEP 2) 
```{r task3_step 2 , include=FALSE}
split <- t(sapply(cil$Code_Postal, function(x) substring(x, first=c(1,2), last=c(2,4))))
cil1<- cbind(cil, split[,1])         
colnames(cil1)<-c( "SIREN","Responsable","Adresse",
                   "Code_Postal","Ville","NAF",
                   "TypeCIL","Portee","Dep")
```
```{r task3_step 2bis}
uniq.cil<-unique(cil1[c("SIREN","Dep")])
head(uniq.cil)
```
```{r task3_step 2ter}
table.uniq<- table(unlist(duplicated(uniq.cil$SIREN)))
table.uniq

```
238 companies dont have a unique cil-responsible per department

STEP 3)
```{r task3_table total}
cil2<-setDT(cil1)

c<-as.character(cil2$SIREN)
cil3<-cbind(cil2,c)
colnames(cil3)<-c("SIREN1","Responsable","Adresse",
                   "Code_Postal","Ville","NAF",
                   "TypeCIL","Portee","Dep","SIREN")
Merge<-merge.data.frame(cil3,SIREN, by="SIREN")
```

STEP 4)
```{r task3_step 4}
summary(Merge$TEFEN)
MergeFactor <- as.factor(Merge$TEFEN)
hist(table(MergeFactor), freq=TRUE, ylab = "Number of companies", xlab="Number of employees / 10", col = "blue")
```
Barely all the companies who nominate a CIL were with less than 100 workers. 